Exploratory data analysis

### 2023-08-07 index.qmd
initial temp trend plots for all stations by year, month, strata in epc data

---
title: "Exploratory data analysis"
author: 
   - name: Marcus Beck, <mbeck@tbep.org>
institute: "Tampa Bay Estuary Program"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    css: styles.css
    code-tools: 
      source: https://github.com/tbep-tech/temp-manu/index.qmd
code-fold: true
execute:
  echo: true
  warning: false
filters:
  - lightbox

@@

```{r}
library(tidyverse)
library(lubridate)
library(EnvStats)
library(tbeptools)
```

>>>>

---
title: "Exploratory data analysis"
author: 
   - name: Marcus Beck, <mbeck@tbep.org>
institute: "Tampa Bay Estuary Program"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    css: styles.css
    code-tools: 
      source: https://github.com/tbep-tech/temp-manu/index.qmd
execute:
  echo: false
  warning: false
filters:
  - lightbox

@@

```{r}
library(tidyverse)
library(lubridate)
library(here)
```

```{r}
knitr::include_graphics('figs/sktall.png')
```

# By month

::: panel-tabset
```{r}
#| results: asis
fls <- list.files(here('figs'), '_', full.names = F)
mos <- fls %>% 
  basename %>% 
  gsub('^skt_|\\.png', '', .) %>% 
  as.numeric() %>% 
  sort() %>% 
  month(label = T) %>% 
  as.character()
for(mo in seq_along(mos)){
  cat('## ', mos[mo], '\n\n')

  chnk <- paste0('![](figs/', fls[mo], ')\n')
  cat(chnk)

  cat('\n\n')

}
```
:::
